### 2017-02-18 docs/reports/experiments_MH-DTM/report_mh-dtm.tex
Adjusting the mac for the latex.@
Adjusting the plotting, implementing the snapshotting, implementing the non auto-regressive variation.

\par This report assesses some experiments performed on reproducing $\alpha$ parameters used in generating synthetic data. Note that the report is structured in the following order: 1) defining the experiment settings; 2) assessing the experiment results.
% ___________________________________________________________________

@@

\begin{figure}[H]
  \centering
  \includegraphics[width=0.5\textwidth]{thetas}
  \caption{The topic assignments to the documents.}
  \label{fig:mu}
\end{figure}

>>>>

\par This report assesses experiments on reproducing $\alpha$ parameters used in the synthetic data generation process. Note that the report is structured in the following order: at the start, the rationale of the used Bayesian methods are covered; then, the experiment settings are defined; in the following stage, we assess the experiment results; finally, the identified issues are outlined to be discussed during the following meeting.
% ___________________________________________________________________

\section*{Preliminaries}

\par In order to understand the experiment experiment settings, it is necessary to be familiar with the auto-regressive and non auto-regressive $\alpha$ priors as well as the Metropolis--Hastings (M--H) algorithm.

\par The previously introduced priors can be expressed as follows:

@@

\begin{figure}[H]
  \centering
  \includegraphics[width=0.5\textwidth]{thetas}
  \caption{The topic assignments to the documents.}
  \label{fig:mu}
\end{figure}
% ___________________________________________________________________
